---
title: "Multi Method Comparison"
author: "Javier Rey"
date: '`r Sys.Date()`'
output: pdf_document
toc: true
---

### Dataset for comparison

```{r load_data, comment = '', echo=FALSE, warning = FALSE, message = FALSE}
data_loaded = data()
n_points = nrow(data_loaded)
label = names(which(dist_options == input$data_input_option))
```
- Dataset:`r label` \
- Data points: `r n_points` \
- Confidence Interval: 95% for all analysis where is required

### Ranking: best test method and linear regression model

Combination test methods vs regression model and its score is sort by better slope (near 1).

```{r ranking, comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE, include=FALSE}
methods = c("LinReg", "WLinReg", "Deming", "WDeming", "PaBa")
# Columns for test methods
column_names = names(data_loaded)
cols_choice_method = sort(column_names[grepl("test", column_names)])

slopes = c()
models = c()
intercepts = c()
test_methods = c()
slope_se = c()
intercept_se = c()  

for (test_method in cols_choice_method) {
    
    for (method in methods) {
        x = data_loaded$reference
        y = data_loaded %>% dplyr::select(!!test_method) %>% pull()
        model = mcr::mcreg(x, y, method.reg=method, mref.name="Reference",
                           mtest.name="Test", na.rm=TRUE, method.ci = "jackknife")
        test_methods = c(test_methods, test_method)
        slopes = c(slopes, round(mcr::getCoefficients(model)[2], digits=2))
        intercepts = c(intercepts, round(mcr::getCoefficients(model)[1], digits=2))
        intercept_se = c(intercept_se, round(model@para[1,"SE"], digits=2))
        slope_se = c(slope_se, round(model@para[2,"SE"], digits=2))
        method_aux = switch(method,
                            "LinReg" = "Ordinary Least Squares",
                            "WLinReg" = "Weighted Ordinary Least Squares",
                            "Deming" = "Deming",
                            "WDeming" = "Weighted Deming",
                            "Passing-Bablok")
        models = c(models, method_aux)
    }
}

df_for_models = data.table(test_method = test_methods,
                           slope = slopes,
                           intercept = intercepts,
                           regression_method = models,
                           intercept_se = intercept_se,
                           slope_se = slope_se)

df_for_models$slope_diff = abs(1 - df_for_models$slope)
df_for_models$slope_error = abs(0 - df_for_models$slope_se)
df_for_models = df_for_models[order(slope_diff, slope_error), ]
df_for_models = df_for_models[, c("test_method", "regression_method", "slope", "intercept")]
df_for_models = purrr::map_df(df_for_models, as.character)
test_method_1 = df_for_models[1, "test_method"]$test_method
model_1 = df_for_models[1, "regression_method"]$regression_method
```

```{r ranking_2, comment = '', echo=FALSE, warning = FALSE, message = FALSE}
pander::pander(df_for_models)
```

### Summary for best test method:

Acording to the above table: \

- Test method: `r test_method_1` 
- Linear regression: `r model_1`

```{r dataframe, comment = '', echo=FALSE, warning = FALSE, message = FALSE, include=FALSE}
library(mcr)

data_loaded = data()
        
methods = c("LinReg", "WLinReg", "Deming", "WDeming", "PaBa")
        
slopes = c()
models = c()
intercepts = c()
 
for (method in methods) {
    x = data_loaded$reference
    y = data_loaded %>% dplyr::select(test_method_1) %>% pull()
    model = mcr::mcreg(x, y, method.reg=method, mref.name="Reference",
                       mtest.name="Test", na.rm=TRUE, method.ci = "jackknife")
    slopes = c(slopes, mcr::getCoefficients(model)[2])
    intercepts = c(intercepts, mcr::getCoefficients(model)[1])
    method_aux = switch(method,
                        "LinReg" = "Ordinary Least Squares",
                        "WLinReg" = "Weighted Ordinary Least Squares",
                        "Deming" = "Deming",
                        "WDeming" = "Weighted Deming",
                        "Passing-Bablok")
    models = c(models, method_aux)
}
df_for_models = data.frame(slope = slopes,
                           intercept = intercepts,
                           model = models)

p = ggplot(data = data_loaded, aes(x = reference, y = y)) + 
    geom_point(colour = "black", fill = "white", shape = 21, stroke = 0.2) +
    geom_abline(data=df_for_models, mapping=aes(slope=slope, intercept=intercept, color=model)) +
    # Identity line
    geom_abline(slope=1, intercept=0, color="red") +
    labs(y=input$method_list) +
    theme_bw(base_size = 12)
```

```{r data_viz, comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE}
p
```

### Model Parameters linear models for best test method

```{r data_param, comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE, include=FALSE}
methods = c("LinReg", "WLinReg", "Deming", "WDeming", "PaBa")

slopes = c()
models = c()
intercepts = c()
data_points = c()
confidence_level = c()
intercept_interval = c()
slope_interval = c()
slope_se = c()
intercept_se = c() 

for (method in methods) {
    x = data_loaded$reference
    y = data_loaded %>% dplyr::select(test_method_1) %>% pull()
    model = mcr::mcreg(x, y, method.reg=method, mref.name="Reference",
                       mtest.name="Test", na.rm=TRUE, method.ci = "jackknife")
    slopes = c(slopes, round(mcr::getCoefficients(model)[2], digits=2))
    intercepts = c(intercepts, round(mcr::getCoefficients(model)[1], digits = 2))
    method_aux = switch(method,
                        "LinReg" = "Ordinary Least Squaress",
                        "WLinReg" = "Weighted Ordinary Least Squares",
                        "Deming" = "Deming",
                        "WDeming" = "Weighted Deming",
                        "Passing-Bablok")
    models = c(models, method_aux)
    data_points = c(data_points, nrow(model@data))
    cl = paste0( ((1 - model@alpha) * 100 ), "%" )
    confidence_level = c(confidence_level, cl)
    ci_intercept = paste0("(", round(model@para[1,"LCI"], digits=2), " - ", round(model@para[1,"UCI"], digits=2), ")")
    intercept_interval = c(intercept_interval, ci_intercept)
    ci_slope = paste0("(", round(model@para[2,"LCI"], digits=2), " - ", round(model@para[2,"UCI"], digits=2), ")")
    slope_interval = c(slope_interval, ci_slope)
    intercept_se = c(intercept_se, round(model@para[1,"SE"], digits=2))
    slope_se = c(slope_se, round(model@para[2,"SE"], digits=2))
}

df_for_models = data.frame(slope = slopes,
                           intercept = intercepts,
                           regression_method = models,
                           intercept_interval = intercept_interval,
                           slope_interval = slope_interval,
                           intercept_se = intercept_se,
                           slope_se = slope_se)

df_for_models = df_for_models[, c("regression_method", "intercept", "intercept_se", "intercept_interval", 
                                  "slope", "slope_se", "slope_interval")]

df_for_models = purrr::map_df(df_for_models, as.character)
```

```{r data_viz_param, comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE}
pander::pander(df_for_models)
```

### Comparability best test method vs reference method

```{r hypothesis, comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE, include=FALSE}
x = data_loaded$reference
y = data_loaded %>% dplyr::select(test_method_1) %>% pull()

# Calc for hypothesis
test_hypothesis = t.test(x = x, y = y, alternative = "two.sided", 
                         conf.level = 1 - 0.05, paired = FALSE, var.equal = TRUE)
```

#### Hypothesis test
$$ H_0 : \\u_1 - \\u_2 = 0 $$ $$ H_1 : \\u_1 - \\u_2 \ne 0 $$
```{r, comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE, include=FALSE}
h_0 = "$H_0$"
```


#### Conclusion \

`r ifelse(test_hypothesis$p.value < 0.05, print(paste0("Reject ", h_0)), print(paste0("Do not reject ", h_0)))`

#### Interpretation

At the `r 0.05 * 100` % significance level `r ifelse(test_hypothesis$p.value < 0.05, print("we reject the null hypothesis that the true difference in means is"), print("we do not reject the null hypothesis that the true difference in means is"))` `r test_hypothesis$null.value` $$ p\\-value $$ `r ifelse(test_hypothesis$p.value < 0.001, print("< 0.001"), print(paste("=", round(test_hypothesis$p.value, 2))))`

### Bland-Altman Visualization

```{r, comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE, include=FALSE}
data_loaded$dif = ( data_loaded %>% dplyr::select(test_method_1) %>% pull() ) - data_loaded$reference
        
y_low = round(mean(data_loaded$dif, na.rm = TRUE) - sd(data_loaded$dif) * 2, digits = 2)
y_up = round(mean(data_loaded$dif, na.rm = TRUE) + sd(data_loaded$dif) * 2, digits = 2)
y_mean =  round(mean(data_loaded$dif, na.rm = TRUE), digits = 2)

p = ggplot(data_loaded, aes(x = reference, y = dif)) +
    geom_point(alpha = 0.5) +
    geom_hline(yintercept = y_mean, colour = "blue", size = 0.5) +
    geom_hline(yintercept = y_low, 
               colour = "red", size = 0.5, linetype="dashed") +
    geom_hline(yintercept = y_up, 
               colour = "red", size = 0.5, linetype="dashed") +
    theme_bw(base_size = 12) +
    labs(title="Difference Plot", x="Reference Method", y="Test(y) - Reference(x)") 
```        

```{r comment = FALSE, echo=FALSE, warning = FALSE, message = FALSE}
p
```

#### Data is processed using R language^1^, shiny web application framework^2^ and mcr package^3^. Shinydashboard^4^and pander^5^ are used for website construction.

##### References and packages:

1.  R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. Version: `r getRversion()` URL: <https://www.R-project.org>
2.  shiny: Web Application Framework for R. Version `r packageDescription("shiny")$Version` URL: <http://CRAN.R-project.org/package=shiny>
3.  mcr: Method Comparison Regression. Version: `r packageDescription("mcr")$Version` URL: <http://CRAN.R-project.org/package=mcr>
4.  shinydashboard: Create Dashboards with 'Shiny'. Version: `r packageDescription("shinydashboard")$Version` URL: <http://rstudio.github.io/shinydashboard>
5.  pander: An R Pandoc Writer. Version: `r packageDescription("pander")$Version` URL: <http://rapporter.github.io/pander>
6.  rmarkdown: Dynamic Documents for R. Version: `r packageDescription("rmarkdown")$Version` URL: <http://rmarkdown.rstudio.com>
7.  data.table: data.table: Extension of data.frame. Version: `r packageDescription("data.table")$Version` URL: <https://CRAN.R-project.org/package=data.table>
8.  dplyr: A Grammar of Data Manipulation. Version: `r packageDescription("dplyr")$Version` URL: <https://CRAN.R-project.org/package=dplyr>
9.  DT: A Wrapper of the JavaScript Library DataTables. Version: `r packageDescription("DT")$Version` URL: <https://github.com/rstudio/DT>
10. plotly: Interactive Web-Based Data Visualization with R, plotly, and shiny. Version: `r packageDescription("plotly")$Version` URL: <https://plotly-r.com>
11. purrr: Functional Programming Tools. Version: `r packageDescription("purrr")$Version` URL: <https://CRAN.R-project.org/package=purrr>
12. shinyBS: Twitter Bootstrap Components for Shiny: `r packageDescription("shinyBS")$Version` URL: <https://ebailey78.github.io/shinyBS/>
13. tinytex: Helper Functions to Install and Maintain TeX Live, and Compile LaTeX Documents: `r packageDescription("tinytex")$Version` URL: <https://github.com/yihui/tinytex/>

